---
title: "Assignment 5 - Meta-analysis of pitch in schizophrenia"
author: "Riccardo Fusaroli"
date: "3/7/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Building on the shoulders of giants: meta-analysis

## Questions to be answered

1. What is the current evidence for distinctive patterns of pitch mean and pitch sd in schizophrenia? Report how many papers report quantitative estimates, your method to analyze them, the estimated effect size of the difference (mean effect size and standard error for pitch mean, same for pitch sd) and forest plots representing it. 
-how many participants

2. Do the results match your own analysis from Assignment 3? If you add your results to the meta-analysis, do the estimated effect sizes change? Report the new estimates and the new forest plots.

3. Assess the quality of the literature: report and comment on heterogeneity of the studies (tau, I2), on publication bias (funnel plot), and on influential studies.

## Tips on the process to follow:

- Download the data on all published articles analyzing pitch in schizophrenia: https://www.dropbox.com/s/pmgw8wzc308so1p/Data.csv?dl=0
- Following the procedure in the slides calculate effect size and standard error of the effect size per each study. N.B. we focus on pitch mean and pitch standard deviation.
 . first try using lmer (to connect to what you know of mixed effects models)
 . then use rma() (to get some juicy additional statistics)

- Build a forest plot of the results (forest(model))
 
- Go back to Assignment 3, add your own study to the data table, and re-run meta-analysis. Do the results change?

- Now look at the output of rma() and check tau and I2
```{r}
pacman::p_load(metafor, plyr, lme4, magrittr,dplyr)
d = read.csv2("Data.csv", stringsAsFactors = F)

# Fix a typo
d = plyr::rename(d, c(SampleSizeContros = "SampleSizeControls"))

# Factors to 
d$PitchMeanControls = as.numeric(d$PitchMeanControls)
d$PitchMeanControlsSD = as.numeric(d$PitchMeanControlsSD)
d$PitchMeanSchizo = as.numeric(d$PitchMeanSchizo)
d$PitchMeanSchizoSD = as.numeric(d$PitchMeanSchizoSD)
d$PitchSDSchizo = as.numeric(d$PitchSDSchizo)
d$PitchSDControls = as.numeric(d$PitchSDControls)
d$PitchSDSchizoSD = as.numeric(d$PitchSDSchizoSD)
d$PitchSDControlsSD= as.numeric(d$PitchSDControlsSD)

PitchRange = escalc('SMD', n1i=SampleSizeSchizo, n2i=SampleSizeControls, m1i=PitchMeanSchizo, m2i=PitchMeanControls, sd1i=PitchMeanSchizoSD, sd2i=PitchMeanControlsSD, data = d)

PitchSD = escalc('SMD', n1i=SampleSizeSchizo, n2i=SampleSizeControls, m1i=PitchSDSchizo, m2i=PitchSDControls, sd1i=PitchSDSchizoSD, sd2i=PitchSDControlsSD, data = d)

# lmer model
mM <- lmer(yi ~ 1 + (1 | Article), weights = 1/vi, data=PitchRange, control=lmerControl(check.nobs.vs.nlev="ignore", check.nobs.vs.nRE="ignore"))
summary(mM)

mSD <- lmer(yi ~ 1 + (1 | Article), weights = 1/vi, data=PitchSD, control=lmerControl(check.nobs.vs.nlev="ignore", check.nobs.vs.nRE="ignore"))
summary(mSD)

# RMA
mM2 = rma(PitchRange$yi, PitchRange$vi, PitchRange, slab = PitchRange$Article)
mM2
mSD2 = rma(PitchSD$yi, PitchSD$vi, PitchSD, slab = PitchSD$Article)
mSD2

# Plant a forest
forest(mM2)
forest(mSD2)

```

```{r}
# Read in data
data = read.csv("../Assignment-3/final_rqa.csv")

data$participant = as.factor(data$participant)
data$study = as.factor(data$study)

# Scale everything
data <- data %>% dplyr::mutate_each_(funs(scale(.) %>% as.vector), 
                             vars = c("mean","stdDev","range","median","InterquartileRange","MeanAbsoluteDeviation","coefficientOfVariation","delay","radius","embed","rqa_REC","rqa_DET","rqa_maxL","rqa_L","rqa_ENTR","rqa_TT","rqa_LAM"))

# Run the model for SD
SD_model = glmer(stdDev ~ diagnosis + (1+diagnosis|participant), data)
summary(SD_model)
# And mean
mean_model = glmer(mean ~ diagnosis + (1+diagnosis|participant), data)
summary(mean_model)

# Try get the numbers you need
## Get the yi
yi_m = fixef(mean_model)[[2]]
yi_sd = fixef(SD_model)[[2]]
## Get the vi
variable = VarCorr(mean_model)
sigmaVisit <- as.numeric(attr(variable[[1]],"stddev")[2])
vi_m = sigmaVisit^2
# And SD
variable = VarCorr(SD_model)
sigmaVisit <- as.numeric(attr(variable[[1]],"stddev")[2])
vi_sd = sigmaVisit^2

# Add these numbers to the PitchRange
# New row for mean
mystudy_mean = c("Mystudy mean", 2017, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, yi_m, vi_m)
PitchRange2 = rbind(PitchRange, mystudy_mean)
# And for SD
mystudy_SD = c("Mystudy SD", 2017, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, yi_sd, vi_sd)
PitchSD2 = rbind(PitchSD, mystudy_SD)

# Factors to numbers
PitchRange2$yi = as.numeric(PitchRange2$yi)
PitchRange2$vi = as.numeric(PitchRange2$vi)
PitchSD2$yi = as.numeric(PitchSD2$yi)
PitchSD2$vi = as.numeric(PitchSD2$vi)

# RMA again
mean2 = rma(PitchRange2$yi, PitchRange2$vi, PitchRange2, slab = PitchRange2$Article)
mean2
SD2 = rma(PitchSD2$yi, PitchSD2$vi, PitchSD2, slab = PitchSD2$Article)
SD2

# Plant 2 more forests
forest(mean2)
forest(SD2)

sum(PitchRange$SampleSizeControls, na.rm=T)

```

3. Assess the quality of the literature: report and comment on heterogeneity of the studies (tau, I2), on publication bias (funnel plot), and on influential studies.
```{r}
# Test for influential studies
inf = influence(mean2)
infSD = influence(SD2)

print(inf)
print(infSD)

plot(inf) #10
plot(infSD) #9

# Funnel plots
funnel(mean2, main = "Random-Effects Model",xlab = "Standardized Mean Difference of Pitch Mean")
regtest(mean2)

funnel(SD2, main = "Random-Effects Model",xlab = "Standardized Mean Difference of Pitch SD")
regtest(SD2)

```

